---
params:
  lesson: "Lesson 1.1"
  title: Using 想 and 要     
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "想，要"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Auxiliary verb   
想/要 + V    

\  

******      
  
## Test question        

我想去长城。    
I want to go to the Great Wall.    

我想吃鸡和饺子。     
I want to eat chicken and dumplings.    

我要回日本。我要参加哥哥的婚礼。      
I want to return to Japan. I want to attend my brother's wedding.   

******   

你要去哪儿？ 
Where are you going (immediately)?  

我要去上海旅行。   
I want to travel to Shanghai (intention).    

我很想吃上海菜。  
I really want to eat Shanghai food.  


\  

******      
    
## Examples   


### 想 
Used to express ideas, wishes, or thoughts    
- long term  
- general  

我想睡觉。        
I want to sleep.  

我想吃蛋糕。   
I want to eat cake.      

我想当警察。  
I want to be a policeman.  

### 要  
Used to express an immediate plan or decision  
- short term  
- specific  

我要睡觉。  
I want to sleep.  

我要借这本书。  
I want to borrow this book.  

劳驾。我要下车。    
Excuse me. I want to get off (the train).     
   
\  

******      
  
## Quiz  

1.  
大(Dà)卫(wèi)的(de)生(shēng)日(rì)快(kuài)到(dào)了(le)。  
我(Wǒ)要(yào)送(sòng)他(tā)一(yī)个(ge)礼(lǐ)物(wù)。  

2.  
我(Wǒ)很(hěn)喜(xǐ)欢(huan)旅(lǚ)游(yóu)。  
我(Wǒ)想(xiǎng)买(mǎi)一(yī)个(ge)旅(lǚ)行(xíng)包(bāo)。  
3.  
快(Kuài)考(kǎo)试(shì)了(le)。  
我(Wǒ)要(yào)好(hǎo)好(hǎo)复(fù)习(xí)。  

4.  
明(Míng)天(tiān)是(shì)周(zhōu)末(mò)。  
你(Nǐ)想(xiǎng)去(qù)看(kàn)电(diàn)影(yǐng)吗(ma)？    

5.  
我(Wǒ)的(de)朋(péng)友(you)病(bìng)了(le)。  
我(Wǒ)要(yào)陪(péi)她(tā)去(qù)医(yī)院(yuàn)。  

Choose the correct question for the answer.  

6.
q: 你(Nǐ)想(xiǎng)吃(chī)中(zhōng)餐(cān)还(hái)是(shì)西(xī)餐(cān)？  
a: 我(Wǒ)喜(xǐ)欢(huan)吃(chī)中(zhōng)餐(cān)。      

7.  
q: 明(Míng)天(tiān)早(zǎo)上(shang)你(nǐ)想(xiǎng)去(qù)跑(pǎo)步(bù)吗(ma)？     
A：太(Tài)早(zǎo)了(le)。我(Wǒ)不(bù)想(xiǎng)起(qǐ)床(chuáng)。    

8.  
q: 你(Nǐ)要(yào)去(qù)银(yín)行(háng)做(zuò)什(shén)么(me)？  
A：我(Wǒ)要(yào)去(qù)银(yín)行(háng)换(huàn)钱(qián)。  

9.  
q: 我(Wǒ)们(men)的(de)衣(yī)服(fu)特(tè)别(bié)好(hǎo)，你(nǐ)要(yào)买(mǎi)一(yī)件(jiàn)吗(ma)？  
A：不(Bù)好(hǎo)意(yì)思(si)，我(wǒ)不(bù)想(xiǎng)买(mǎi)。  

10.  
q: 周(Zhōu)末(mò)你(nǐ)想(xiǎng)去(qù)爬(pá)山(shān)吗(ma)？   
A：恐(Kǒng)怕(pà)不(bù)行(xíng)，周(zhōu)末(mò)我(wǒ)要(yào)学(xué)习(xí)。  

