---
title: Chinese MOOC 
author: |
 | Matt Malishev  
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
fontsize: 10
geometry: margin=1in
documentclass: article
linkcolor: blue
urlcolor: blue
citecolor: red
output:
  html_document:
    highlight: tango
    code_folding: hide
    code_download: true
    toc: yes
    toc_depth: 4
    number_sections: no
    toc_float: yes
  pdf_document:
    includes:
      in_header: # add .tex file with header content
    highlight: tango
    template: null
    toc: yes
    toc_depth: 4
    number_sections: false
    fig_width: 4
    fig_height: 5
    fig_caption: true
    df_print: tibble 
    latex_engine: xelatex #pdflatex # lualatex
    keep_tex: false # keep .tex file in dir 
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
inludes:
  # before_body: before_body.tex
subtitle: 
tags:
- nothing
- nothingness
params: 
  dir: "/Users/malishev/Documents/chinese/mooc/chinese_mooc"
  date: !r Sys.Date()
  session: !r sessionInfo()  
  version: !r getRversion()
  email: "matthew.malishev@gmail.com"
  doi: https://moocs.unipus.cn/my/course/373  
classoption: portrait
# ^['https://github.com/darwinanddavis/UsefulCode'] # footnote
vignette: >
  %\VignetteIndexEntry{Useful R code}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\newpage   

Date: `r params$date`  
R version: `r params$version`   
*Corresponding author: `r params$email`  
This document can be found at `r params$doi`  

\  

R session info 

```{r, echo=F}
params$session
```      

\newpage  

# Lesson 1  

## Auxiliary verbs 能，会，可以  
- modify verbs and actions    
- negate with 不  

### 能  
- expresses ability  
- expresses possibility due to circumstance   

他不能走路  
He can't walk  
他能走路  
He can walk  

### 会    
- expresses grasp of skil from learning    
- expresses possibility    

今天不会下雨  
Today it won't rain  

### 可以   
- expresses permission  

我可以用一下你的自行车吗？   
Can i use your bike?  

Pose a question with auxiliary verbs by
- using the positive and negative form  
- using 吗


我可以不可以进去 / 我可以进去吗？  









