---
params:
  lesson: "Integrated Chinese - Lesson 11"  
  title: "天气"            
  link: "https://sites.google.com/site/zhongwentingshuoduxie/di-shi-yi-ke-tan-tian-qi/yu-fa-dong-hua"  
  content: "天气"  
  date: !r Sys.Date()
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  


# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`     

### 不但 。。。 而且 。。。  
Not only ... but also ...  
不但不会下雪，而且会暖 和一点儿。   
Not only will it not snow, but it will be a little warmer.    

## Comparative sentences  

### 比 。。。一点儿/得多/多了  
A + 比 + B + ADJ + 一点儿/得多/多了    
今天比昨天冷一点。  
Today is a bit colder than yesterday.  

明天比今天冷得多。   
Tomorrow will be much colder than today.  

纽约比这儿冷多了。  
New York is much colder than here.  
* Note the modifying expression is placed after the ADJ    

### 比。。。更/还 + ADJ  
A + 比 + B + 更/还 + ADJ   
昨天冷。 今天比昨天更冷。（更）      
昨天冷。 今天比昨天还冷。（还）      
Yesterday was cold. Today is even colder than yesterday.    

### Grammar  
天气预报 forecast   

### Examples  
天气预报说北京明天会下雪。  
The weather forecast says it will snow tomorrow in Beijing.  

昨天纽约不下雨了。    
It didn't rain in NY yesterday ??  

我觉得北京跟上海一样冷。  
不，上海比北京热多了。  
I think Beijing is as cold as Shanghai.  
No, Shanghai is much hotter than Beijing.  




