---
params:
  lesson: "Lesson 5.5"
  title: "Verb complements"              
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: ""  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Explaining 'can or can not'    
。。。V + 得 + result 。。。 V + 不 + result         
is the same as the following combined:    
能 + V + result 吗?      
能不能 + V + result?         

A = B + C combined    
他们吃得完吃不完? A  
Can you or can you not finish eating? 

Is the same as the following combined:     
他们能吃完吗？B  
他们能不能吃完？C      
Can they finish eating?  
Can they finish eating or not?  


他们啃得懂看不懂？A    
他们能看懂吗？B  
他们能不能看懂 C    
  

\  

******      
  
## Test question        

你说的太快了，我听不懂。   
You spoke too fast, I don't understand.    
  
\  

******      
    
## Examples   

他们吃得完吃不完？ 
他吃得完。    
他吃不完。   
Can they or can't they finish eating?    
He can finish eating.    
He can't finish eating.    
  
他们看得懂看不懂？    
他看得懂。    
他看不懂。   
Can they or can't they understand?     
He does understand.    
He does not understand.    

他们看得清楚看不清楚？    
他看得清楚。      
他看不清楚。     
Can or can't they see clearly?      
He can see clearly.    
He can't see clearly.      

今天的作业太多了。   
我写不完。     

你说什么？  
我听不见。    

你怎么不进去？  
我找不到钥匙了，进不去。  
Why don't you enter?  
I can't find the key, I can't enter.  






\  

******      
  
## Quiz  
  
1.   
今天  的 语法 太 难 了，我__________。  
听 不 懂

2.  
我 喝 了很  多  咖啡，晚上__________ 。  
睡 不 着  

3.  
去 旅游 的 人 太多了，飞机票  都 卖  完 了， 我__________。  
买 不 到 票  

4.  
房 间  里 太黑了， 我__________，打 开  灯 吧。  
看 不 见      


5.  
不 好 意思， 明 天  有 考 试， 你的  生 日 晚 会 我__________。  
去不了  

TRUE OR FALSE  

6.  
爷爷 老了，报 纸  上  的字 看 得不 清楚。  
F  

7.  
我 的 手机  坏了，修 得 好 修 不 好？  
T  

8.  
汉字 太 难 了， 我记 不 住。  
T  

9.  
路 上   堵车，  我  晚饭  以前 不能   回去。  
F    

10.  
地铁 里的人 太 多 了，我   上 不 去。  
T  

