---
params:
  lesson: "Lesson 3.4"
  title: "Comparative sentences III：A+V+得+比+B+ADJ / A比B+V+得+ADJ"         
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "比"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

主讲老师雷朔    

Express the extent of a verb when comparing two people/things       

Option 1   
A does verb compared to B by this extent (ADJ)      
A + V + 得 + 比 + B + ADJ      

Negative form: replace 比 with 没有 using the same ADJ       
N + V + 得 + 没有 + N + ADJ        

Option 2    
A compared to B does verb by this extent (ADJ)  
A + 比 + B + V + 得 + ADJ  

Negative form: replace 比 with 没有 using the same ADJ     
A + 没有 + B + V + 得 + ADJ   

\  

******      
  
## Test question        

我篮球打得比大卫好。  
I play basketball better than David.  

大卫足球踢得比我好。  
David kicks a football better than me.   


\  

******      
    
## Examples   

#### 1  

Option 1  
我穿得比大卫多。   
大卫穿得比我少。  
大卫穿得没有我多。 （negative form)  
I wear more than David.    
David wears less than me.  
David wears less than me.    

Option 2  (N) = implicit part  
我(衣服)比大卫穿得多。            
大卫没有我穿得多.（negative form)      
I wear more (clothes) than David.   
David wears less than me.     

#### 2  

Option 1  
我做饭做得比食堂做饭做得好吃。   
I cook better than the cafeteria.  

Option 2  
我没有我的妈妈做得好吃。      
I don't cook as well as my mum.    

#### 3    

Option 1   
我的口语考试考得比你好。     
My oral exam is better than yours.    

Option 2    
你的听力考试比我考得好。          
Your listening exam is better than mine.      

你的字写得比我漂亮多了。  
Your handwriting is more pretty than mine.   

#### Summary  

Situation:  
大卫考了100分我80考了分。  
David scored 100 points, I scored 80 points.    

大卫考得比我好。A + V + 得 + 比 + B + ADJ（option 1)    
大卫比我考得好。A + 比 + B + V + 得 + ADJ（option 2)   
David scored better than me.   

Situation:  
大卫是七点半来的，我八点来的。   
David came at 7.30, I came at 8.  

大卫来得比我早。A + V + 得 + 比 + B + ADJ（option 1)    
大卫比我来得早。A + 比 + B + V + 得 + ADJ（option 2)  
David came earlier than me.  

### 2  

Situation  
妈妈做饭特别好吃， 我做饭很一般。   
My mum's cooking is particularly delicious, my cooking is average.  

妈妈(做)饭做得比我好吃。 A +（V）+ O + V + 得比 + B + ADJ (option 1)      
妈妈(做)饭比我做得好吃。A +（V）+ O + 比 + B + V + 得 + ADJ (option 2)       
Mum cooks better than me.      

Situation  
大卫的字写得很漂亮， 我的字写得不太漂亮。    
David's handwriting is very pretty, my handwriting is not so pretty.    

大卫(写)子写得比我漂亮。A +（V）+ O + V + 得比 + B + ADJ (option 1)            
大卫写子比我写得漂亮。A +（V）+ O + 比 + B + V + 得 + ADJ (option 2)        
David writes more pretty than me.    

### Negative forms  

我字写得没有大卫漂亮。  
我字没有大卫写得漂亮。   
My writing is not as pretty as David's.    

## Grammar exercises      

他睡得比他的妻子早。（option 1)    
他比他的妻子睡得早。（option 2)         
He went to sleep earlier than his wife.        

他喝得比我多。（option 1)          
他比我喝得多。（option 2)            
He drank more than I did.    

他开得比我好。（option 1)       
他比我开得好。（option 2)        
He drives better than me.    

我汉语说得比他好。（option 1)        
我汉语比他说得好。 （option 2)     
I speak Chinese better than him.        
  
\  

******      
  
## Quiz  

Choose the negative form  
  
1.  
我比弟弟开车开得快。  
弟弟没有我开得快。 

2.  
这几天他减肥，所以我吃得比他多。  
他没有我吃得多。    

3.  
今天太冷了，我穿得很少，他比我穿得更少。  
我衣服穿得没有他少。    

4.    
这个月安妮花了2000元，大卫花了5000元。  
安妮没有大卫花得多。

5.  
大卫喜欢看书，他知道很多中国的故事。山本看得少，不太了解中国。  
山本没有大卫知道得多。  

**判断正误**    

6.    
我骑车比他骑得快。    
TRUE    

7.  
我没有安妮用筷子得好。  
FALSE    

8.  
虽然奶奶60岁了，可是我走路没有她快。    
TRUE  

9.  
他来中国三年了，比我知道得多。  
TRUE  

10.  
我的同屋比我每天都回来得晚。  
FALSE    

