---
params:
  lesson: "Lesson 5.3"
  title: "Simple directional complements"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "来，去"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

### 来  
Indicates the direction of action towards the speaker  
来教室  
来宿舍  
  
### 去  
Indicates the direction of action against the speaker  
去学校  
许食堂  


\  

******      
  
## Test question        

我可以进去吗？   
Can I go in?    
快进来吧。     
Come in quickly.  

**Scenario 1**  

你快下来，我们一起去吃饭吧。   
我不下去了， 我包了饺子，你上来吧，我们一起吃饺子。  
Come down， let's go eat together.    
I can't go down, I made dumplings. You come up here, let's eat dumplings together.      

**Scenario 2**  

大卫快请进来了。   
我不进去了，你可以出来吗？      
David, quickly please come in.  
I can't come in, can you come out?      

**Scenario 3**    
你可以过来吗？   
可以， 我马上过去。   
Can you come over?  
I can, I will go immediately.  

**Scenario 4**      
我忘了作业，我要马上回去。    

I forgot my homework, I want to go back immediately.    


\  

******      
    
## Examples   

  
Going up stairs (A - B)  
大卫上来了。(A - B)      
大卫上去了。(B - A)      
David came up.      
David went up.      

Going down stairs (A - B)  
大卫下去了。（A - B)    
大卫下来了。（B - A）    
David went down.  
David came down.  

Coming into a room (A - B)  
大卫进来了。 (A - B)  
大卫进去了。（B - A)  
David came in.  
David went in.  

Going out of a room (A - B)  
大卫出去了。 (A - B)  
大卫出来了。（B - A)    
David went out.  
David came out.  

Going to a location (A - B)    
大卫过来了。 (A - B)  
大卫过去了。(B - A)    
David is coming.  
David went away.    

Returning to a location (A - B)  
大卫回来了。（A - B）   
大卫回去了。 （B - A)  
David came back.  
David went back.  

There is no 去 when using 起, only 来， i.e. 起床      
大卫起来了。   
David got up.    

### 来  

他们跑来了。    
他们走来了。   
他送来了很多礼物。   
他给我拿来了一杯咖啡。    
姐姐从超市回来了。  
They ran.    
They came.    
He sent many gifts.    
He brought me a cup of coffee.    
My sister came back from the supermarket.      

\  

******      
  
## Quiz  
  
Fill in the blank.  

1.  
外面太冷了，咱们(1)吧！    
进去    


2.  
他去旅行了，下星期(1)。  
回来  

3.  
山上一定很漂亮，咱们快(1)吧！  
上去  

4.  
哎，山上的风景美极了，你们快点儿(1)啊！  
上来  

5.    
她还没(1)呢，你过一会儿再来电话吧。  
回来   

TRUE OR FALSE

6.  
你看！车站在马路那边，你快过来吧。    
F  

7.  
图书馆要关门了，我们回去吧。    
T    

8.  
房间里特别暖和，你们别在外面聊天了，快出去吧。  
F 

9.  
大(Dà)卫(wèi)，我(Wǒ)在(zài)楼(lóu)下(xià)等(děng)你(nǐ)，你快点下去 。  
F 

10.  
我(Wǒ)饿(è)了(le)，要出去买点儿吃的。    
T 

