---
params:
  lesson: "Lesson 6.3"
  title: "把 + V + 给"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "把， 给"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Describing something reaching somewhere through certain actions.  

### S + 把 + O + V + 给 + something    
### S + 没 + 把 + O + V + 给 + something （negative form)     

\  

******      
  
## Test question        

我想吃烤鸭请把烤鸭递给我。  
I want to eat roast duck, please pass me the roast duck.  

我想把茶叶送给爸爸。    
I want to give tea to dad.    

我想把旗袍送给妈妈。  
I want to give the cheongsam to mum.  

我没把球扔给他。   
I didn't throw the ball to him.    

\  

******      
    
## Examples   

请大家把作业本交给我。  
Please everyone give me your workbook.  

我把照片发给妈妈了。  
I sent the photo to my mum.  

我没把花送给你。     
I didn't give you the flowers.  


\  

******      
  
## Quiz  

Choose the correct sentence.    
  
1.  
售(Shòu)货(huò)员(yuán) 把(bǎ) 钱(qián) 退(tuì) 给(gěi) 我(wǒ) 了(le)。  


2.  
玛(Mǎ)丽(lì) 没(méi) 把(bǎ) 邮(yóu)件(jiàn) 发(fā) 给(gěi) 老(lǎo)师(shī)。

3.  
我(Wǒ) 把(bǎ) 那(nà)套(tào) 房(fáng)子(zi) 卖(mài) 给(gěi) 他(tā) 了(le)。  

4.    
你(Nǐ) 一(yí)定(dìng) 要(yào) 把(bǎ)  这(zhè)本(běn) 书(shū) 带(dài) 给(gěi) 他(tā)。

5.  
请(Qǐng) 把(bǎ) 英(yīng)汉(hàn) 词(cí)典(diǎn) 递(dì) 给(gěi) 我(wǒ)。  

TRUE OR FALSE  

6.  
他(Tā) 送(sòng) 花(huā) 给(gěi) 妈(mā)妈(mā) 了(le)。  
F  

7.  
小(Xiǎo)王(wáng) 借(jiè)钱(qián) 给(gěi) 我(wǒ) 了(le)。  
F 

8.  
我(Wǒ)们(men) 都(dōu) 把(bǎ) 作(zuò)业(yè) 交(jiāo)给(gěi) 老(lǎo)师(shī) 了(le)。  
T 

9.  
我(Wǒ) 忘(wàng)了(le) 把(bǎ) 照(zhào)片(piàn) 发(fā) 给(gěi) 张(Zhāng)东(dōng) 了(le)。  
T 

10.  
大(Dà)山(shān) 把(bǎ) 球(qiú) 没(méi) 踢(tī) 给(gěi) 大(Dà)卫(wèi)，他(tā) 踢(tī) 给(gěi) 飞(Fēi)龙(lóng) 了(le)。  
F  

