---
params:
  lesson: "Lesson 7.3"
  title: "Interrogative pronoun in a rhetorical question"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: ""  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Using interrogative pronouns (who, what, why) to express strong tones or emotions  
Can be used to make a negative, questioning sentence, e.g.  

- Who cares? 
- Who knows?  
- Why wouldn't I?  

\  

******      
  
## Test question        

A: 今天是我的生日。你忘了吗？    
B: 我怎么会忘吗？      
Today is my birthday. Did you forget?      
How could I forget?      

\  

******      
    
## Examples   

A: 老板怎么了？
B: 谁知道.     
What happened to the boss?   
Who knows.  
谁知道 --> 不知道     

我只有一块钱了。 我能买什么？    
I only have 1 kuai. What can I buy?    
我能买什么？--> 不能买    

你只十岁。你怎么能喝酒呢？      
You are just 10 years old. How can you drink alcohol?   
你怎么能喝酒呢？--> 不能喝酒       

中文的女人这么可爱，谁不喜欢？   
Chinese women are so cute, who doesn't like them?  

没错。我哪儿没去过？   
Not wrong. Where have I not been?  

你怎么会看不懂？    
How can you not understand?  
    
我怎么知道呀？   
How should I know?  
    
******    

你喜欢看电影吗？    
谁不喜欢看电影。    

我看过所有的电影。     
我什么电影没看过？  
I have watched all the movies.    
What movie have I not seen?   
  
当然看得懂。我怎么会看不懂?  
Of course I understand. How could I not understand?  
  
\  

******      
  
## Quiz  
  
1.  
A：今天他 为什么   不 高兴？    
我____知道？  
怎么  

2.  
A：明天  你 不去  上海   出差  吗？     
B：明天  是  周末。   
_____想  出差  啊？  
谁  

3.  
A:  广州    冬天   下 雪  吗？   
B：广州    在  南方。 _____有 雪？  
哪儿  

4.  
A：这个字 怎么读？ 
B：老师   刚   教过，你_____不 知道？  
怎么  

5.  
A：他 爱吃  这个 吗？   
B：当然。他_____不 爱吃？  
什么    

Choose the correct meaning of the bold sentence.    

6.  
我  还是  学生， **我 哪 儿 有 这么 多 钱？**    
我  没有   这么  多  钱。  

7.  
他 这么 有名，**谁 不 认识 他**  
所有 人 都  认识 他。     

8.  
今天 放假 了，**公司里 哪儿 有 人？**  
公司 里  没有  人。  

9.  
这么好的机会，**谁不想去**  
每 个 人 都  想  去。    

10.  
他 是  新 来 的，**他  知道  什么？**      
他 不 知道。   

