---
params:
  lesson: "Lesson 4.3"
  title: "Concurrent statements"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "请，叫，让"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

### 请  
to treat  
to ask something politely (SUBJECT = 你 or 你们)      
请 + SUBJECT + V + OBJ1      

### 叫  
to ask/tell     
叫 + SUBJECT + V + OBJ1     

### 让  
to ask        
让 + SUBJECT + V + OBJ1     

\  

******      
  
## Test question        

### 请    
我请你吃饭。  
我请你看电影。  
I invite you to eat.  
I invite you to watch a movie.  

请你小声说话。       
Please speak quietly    

### 叫    
他叫你关窗户。  
He told you to close the window.  

### 让    
老师让我们写生词。        
The teacher asked us to write new words.       

\  


******      
    
## Examples   

### 请  
这里太热了。请你把空调打开吧。  
It's too hot here. Please turn on the airconditioner.  

### 让  
我去图书馆。大卫让我给他借一本书。  
I'm going to the library. Dawei asked me to borrow him a book.  

### 叫  
这是你叫我借的书。    
This is the book you asked me to borrow.  

大卫叫我去他那儿。      
Dawei told me to go to him.      


\  

******      
  
## Quiz  
  
1.  
上课的时候，老师让同学们__________。  
读课文  

2.  
妈妈说她很忙,没时间做饭，她叫我__________。  
做饭  

3.  
马丁，__________。  
请你告诉玛丽  

4.  
明天有个好看的电影，我__________。  
请你看电影

SELECT THE CORRECT SENTENCE  

5.  
太吵了，请大家安静。  

TRUE OR FALSE  

6.  
刮风了，请你关门。  
T  

7.  
太吵了，让你安静。  
F    

8.    
晚上朋友请我电影。  
F   

9. 
妈妈叫他回家。  
T 

10.  
爸爸请他做饭。  
F  

