---
params:
  lesson: "Lesson 3.3" 
  title: "Comparative sentences II: comparing precise quantity"
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "比"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Express the quantity/number difference between two things  
。。。比。。。 + ADJ + quantity/number       
N + 比 + N + ADJ + quantity/number       

\  

******      
  
## Test question        

坐飞机比坐火车贵五百块。  
It's 500快 more expensive by plane than train.  

坐飞机比坐火车快两个多小时。  
It's more than 2 hours faster travelling by plane than train.       

\  

******      
    
## Examples   

大卫比我大。  
大卫比我大三岁。  
David is 3 years older than me.  

今天比昨天气温高。      
今天比昨天高四度。        
The temperature is higher today than yesterday.    
Today is four degrees higher than yesterday.    

我今天比去年胖了。  
我今天比去年胖了五公斤。  
I am fatter this year than last year.      
I am 5 kilos fatter this year than last year.  

这个咖啡比那个茶贵四元。  
This coffee is 4 yuan more expensive than that tea.  

我比大卫重五公斤。  
I am 5 kilos heavier than David.  

一班比二班多五个学生。    
There are 5 more students in class 1 than class 2.  

\  

******      
  
## Quiz  

1.  
他比我________。  
重五公斤  

2.  
麦克比山田_______。  
大两岁  

3.  
这件大衣比那件________。  
贵300块    

4.  
超市比商场远________。  
200多米  

5.  
这个杯子比那个杯子________。  
贵20块  

TRUE OR FALSE  

6.  
红苹果比黄苹果贵两块。  
TRUE  

7.  
十月比九月一天多。  
FALSE  

8.  
今天突然比昨天低了十多度。  
TRUE   

9.  
这个房间贵一百块比那个房间。  
FALSE  

10.  
我的生日是7月28号，比妈妈的生日早一天。  
TRUE  





