---
params:
  lesson: "Lesson 3.2"  
  title: Comparative sentences            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "比"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  


# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Compare two people or things or actions to describe the difference    
。。。 比 。。。 + ADJ  
E.g.  
N + 比 + N + ADJ  
V + 比 + V + ADJ    
The adjective describes the comparison between the nouns/verbs  

\  

******      
  
## Test question        

老北京比小上海干净    
Old Beijing is cleaner than Little Shanghai  

老北京比小上海好吃    
Old Beijing is better (food) than Little Shanghai  

小上海比老北京便宜   
Little Shanghai is cheaper than Old Beijing     

小上海比老北京便近    
Little Shanghai is closer than Old Beijing     

这个咖啡比那个茶贵。   
This coffee is more expensive than that tea    

大卫比我重  
David is heavier than me  

那个菜比这个菜辣  
That dish is spicier than this one    

\  

******      
    
## Examples   


大卫比我高  
David is taller than me.      

今天比昨天热  
It is hotter today than yesterday  

堵车的时候，走路比开车快  
In traffic jams, walking is faster than driving  

\  

******      
  
## Quiz  

Fill in the blanks  

1.  
一年不见，小明比去年更**高**了。  

2.  
我的听力比阅读**好**  

3.  
北京比上海**大**       

4.    
我们打车去吧，打车比坐公共汽车**快**  

5.  
你多穿点儿吧，今天比昨天 **冷**  

TRUE OR FALSE  

6.    
我今年比去年胖 
TRUE  

7.  
爸爸比妈妈很忙  
FALSE   

8.  
学语法比学汉字容易。  
TRUE  

9.  
这个教室比那个教室大  
TRUE  

10.  
这个宾馆舒服比那个宾馆    
FALSE  






