---
params:
  lesson: "Lesson 6.2"
  title: "把"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "把"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Using 把 to express change in something/someone  

### S + 把 + A + V + 成 + B            
把 + A = what the speaker intends to express    
成 + B = what the speaker has already expressed      

\  

******      
  
## Test question        

我要把美元换成人民币。  
I want to exchange US dollars for RMB.  

\  

******      
    
## Examples   

我英语翻译成汉语了。   
我把英语翻译成汉语了。   
I translated English into Chinese.   
I translated English to become Chinese. 

我老师当成好朋友了。    
我把老师当成好朋友了。    
I treat my teacher as a good friend.  
My teacher has become a good friend.       

******  

我把红色的衬衫换成了白色的。   
I changed the red shirt to white.    

我把王老师看成李老师了。   
I considered Mr Wang as Mr Li.    


\  

******      
  
## Quiz  
  
TRUE or FALSE   

1.  
我把护士看你的妹妹成了。  
F     

2.  
我把8点考试记成9点考试了。  
T    

3.  
姐姐把大号的衣服成换中号的了。  
F 

4.  
我把同屋当成哥哥了。  
T 
  
5.  
哥哥把电视听错成电池了。  
F 

6.  
他把汉语翻译成日语了。  
T  

7.    
他把人民币换了成韩元。  
F   

8.  
她换黑色的衣服成了红色的把。  
F 

9.  
她把“睡觉”说成“水饺”了。  
T 

10.  
她把“1”听“7”成了。  
F 

