---
params:
  lesson: "Lesson 2.5"
  title: "Verb phrases and attributes using ‘的’"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "的"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`       

V + 的 + N  
Verb phrase + 的 + Noun phrase  
- Indicates a specific person or thing    

\  

******      
    
## Test questions   
  
大卫在踢足球    
**踢足球的**那个人是大卫    
David is playing football  
The man playing football is David  
    
\  

******      
    
## Examples     

这是蛋糕    
这是**妈妈做的**蛋糕  
This is a cake  
This is mum's cake  

请问哪位是鱼老师？    
**喝咖啡的**那个人是鱼老师    
Which one is teacher Yu?  
Teacher Yu is the one that is drinking coffee.       

我在中国买了一个礼物  
这是**我在中国买的**礼物  
I bought a present in China    
This is the present I bought in China    

\  

******      
    
## Exercises  

这是一张中国拍的照片。  
在中国拍的照片。  
This is a photo taken in China  
It is taken in China      

弟弟手里拿着什么？  
他画的画儿  
What is the younger brother holding?  
The painting he painted   

那个人是太极老师？    
穿白色衣服的老人    
Who is the Tai Chi teacher?  
The old man in white clothes  

\  

******      
    
## Quiz   

Put the words in the correct place  

1.    
"的"  
  
这  A 是  B 姐 姐  C 送  我 D  生 日  礼物。  
这是姐姐送我的生日礼物。  

2.  
"老人"  
  
大家都觉得表演功夫的很了不起。  
大家都觉得表演功夫的老人很了不起。  

3.  
"学生"  

来中国学习汉语的越来越多。  
来中国学习汉语的学生越来越多。  

4.  
"送"  

今天是他的生日, 这些都是朋友的礼物。     
今天是他的生日，这些都是朋友送的礼物。  

TRUE OR FALSE  

5.      
这  是  汉 语 书  大卫  买  的。     
FALSE  

6.  
安妮 写  的  汉 字 很  漂  亮。   
TRUE  

7.  
墙    上    有  一 张    爸爸 画  的 画儿。  
TRUE  

8.  
我最  喜欢   吃  妈妈 做  的 菜。   
TRUE  

9.  
那 个 人  穿    着  白 色 运 动  服 的 是  马 丁。  
FALSE   

10.  
安妮 是  我们  班  汉 语  说   得 最  好  的 学 生。   
TRUE  




  














 
 
 




