---
params:
  lesson: "Lesson 6.5"
  title: "把 with verb and other components"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "把"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

### S + 把 + O + V + complement  

\  

******      
  
## Test question        

你把这些杯子洗一洗。    
You wash these cups.  

你把地嫂嫂。  
You sweep the floor.    
 

\  

******      
    
## Examples   

我把菜尝了尝。    
I tasted the dishes.  

你快点儿把东西收拾收拾。  
You quickly pack up the things.  

我把垃圾扔了。    
I threw away the garbage.  

你把这件衣服试一试。  
You have to try on these clothes.       

******  

我把黑板擦了。   
I wiped the blackboard.    

你把这件衣服洗一洗。    
Wash these clothes.  

\  

******      
  
## Quiz  
  
1.    
我把做好的菜都吃了。    

2.    
你下课后就把作业改一改。  

3.  
大卫，请你把前边的门关一下。 

4.  
师傅，请你把这辆自行车修一下。  

5.  
明天是弟弟的生日，我想把房间布置一下。    

6.  
张红把苹果吃吃。  
F 

7.  
爸爸把钱数了数。  
T 

8.  
服务员把垃圾收一收了。  
F 

9.  
你把课文复习一下。  
T 

10.  
弟弟把书看看了。  
F 

