---
params:
  lesson: "Lesson 5.1"
  title: "Time complements"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: ""  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

V + time duration （+ optional NOUN)     
Time duration can be placed after the verb   
e.g. 

吃了 + 二十个小时。  
睡了 + 十分钟。  
学习 + 两个小时 + 汉语。    
  
\  

******      
  
## Test question        

从上海到北京要坐六个小时的火车。      
From Shanghai to Beijing takes 6 hours by train.  

到宾馆以后同学们好好休息一个晚上，明天开始参观。   
After arriving at the hotel the students take a good rest during the evening, and start their visit tomorrow.      

我们一共要在上海游览三天。  
We will tour Shanghai for three days total.  
  
\  

******      
    
## Examples   

大卫要在中国学习一年汉语。  
David wants to be in China to study Chinese for one year.   

他每天写作业要花两个小时。  
He spends two hours everyday doing homework.  

昨天作业很多，他写了一晚上的作业。  
Yesterday there was a lot of homework, he wrote homework for one evening.  

今天上课他很困，睡了十分钟。  
He was very tired in class today and slept for 10 minutes.    

******  

### Exercises  

我每天学三个小时汉语。        

从我的国家到北京要坐十个小时的飞机。    
It takes ten hours to fly from my home country to Shanghai.    

我等了半天公共汽车，车才来。    
I waited for the bus for half a day before the bus came.      



\  

******      
  
## Quiz  

Complete the sentence using the bracketed words  
  
1.  
我每天(1) 。   （写 汉字       一个小时）  
写一个小时汉字   

2.  
我每天睡觉以前(1)。（看 书    一会儿）  
看一会儿书    

3.  
从我家去学校要(1)。（坐 公共汽车         半个小时）    
坐半个小时的公共汽车  

4.  
明年我打算去中国(1)。（学习 汉语         四个月）    
学习四个月汉语      

5.  
昨天是我的生日，我跟朋友们(1)。      （喝 啤酒     一晚上）      
喝了一晚上啤酒  
  
6.  
我病了一个星期，今天好了。  
TRUE  

7.  
昨天我病了，一天睡觉了。  
FALSE  

8.  
我每天下午两个小时运动。   
FALSE  

9.  
爬山太累了，我们休息一会儿吧。  
TRUE 

10.  
考试以前，我一个月复习了。  
FALSE 

