---
params:
  lesson: "Lesson 2.2"
  title: "Using ‘地’字结构"        
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "地"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`    

ADJ/ADV + 地 + VERB/verb phrase     
- describes how the action is finished   
- used for general action statements  

\  

******      
  
### Test question      

孩子高高兴兴地去上学了。  
The children went to school happily  

我努力地写汉字。  
I am writing Chinese characters carefully     

我大声地唱歌。  
I am singing loudly  

他轻轻地走进了教室  
She went to the classroom quietly    

今天晚上我要美美的吃一顿烤鸭    
I want to eat a lovely roast duck tonight    

\  

******      
  
## Exercises  

教室大家正在安静地考试    

那些人缓慢地做太极拳动作    

我最近太累了真想舒舒服服地睡一觉   

\  

******      
  
## Quiz    

1.  
安静地  
考试  

2.  
缓慢地  
打太极拳

3.  
认真地  
写汉字， 考试， 给他号脉  

4.  
生气地  
出去了， 回家了  

5.  
高兴地  
写汉字， 回家了  

6.  
美美地  
吃一顿  

7.  
安静地  
教室里大家正在安静地写作业。

8.  
高兴地  
每天孩子们都去学校上学  
每天孩子们都高兴地去学校上学。  
  
9.  
美美地  
那个饭馆的菜真好吃，昨天我们美美地吃了一顿。  

10。    
舒舒服服地  
最近我太累了，真想舒舒服服地睡一天。  


  









