---
params:
  lesson: "Lesson 4.1"
  title: Linking sentences - representation    
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: ""  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Preceding a verb with another verb   


\  

******      
  
## Test question        

你怎么来学校？   
我走路学校。   
我开车来学校。  
How did you come to school?    
I walk to school.    
I drove to school.    

你怎么回家？ 
我打的回家。  
How do you go home?  
I take a taxi.      
 

\  

******      
    
## Examples   



我回宿舍。  
你怎么回宿舍？  
我走路回宿舍。   
I'm returning to the dorm.  
How do you return to the dorm.  
I walk to the dorm.  

我骑自行车去超市。  
I ride a bike to the supermarket.  

我去超市买东西。  
我骑自行车去。  
I'm going to the supermarket to buy things.  
I go by bike.  

我坐火车去上海。  
我坐飞机去上海。  
I take the train to Shanghai.  
I fly to Shanghai.    



\  

******      
  
## Quiz  
  
Insert the missing word  

1.    
怎么  
A 安妮 B 每天  早上  C 来  学校 D？  
安妮每天早上怎么来学校？  

2.  
骑 自 行 车  
A 这个  周末 B  我们 C 去  公 园    玩儿 D。  
这个周末我们骑自行车去公园玩儿。  

3.  
回  
A下 个 星期 B 我 C 坐 飞机 D 国。  
下个星期我坐飞机回国。  

4.  
开  车  
爸爸 A 每  天   早上 B 去 C  公 司 D 工 作。  
爸爸每天早上开车去公司工作。  

TRUE OR FALSE    

5.  
我们  明  天   怎么  学 校   去？  
FALSE  

6.    
我  想   坐  飞机  去  上 海   旅 行。  
TRUE    

7.  
马丁  每  天   早 上   来  学  校  走路。  
FALSE  

8.  
坐 公 共 汽 车   去 颐和园   太  挤 了。  
TRUE  

9.  
大卫  和 马 丁  明  天   去 坐  火 车  天  津。  
FALSE  

10.  
那 个 饭馆儿   很  远，  打 的 去  太 贵  了。  
TRUE  

