---
params:
  lesson: "Lesson 7.4"
  title: "Using interrogative pronouns to express arbritrary reference"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "都， 也"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

### 都 & 也    

Creating an affirmative or negative statement with interrogative pronoun, e.g. 谁， 哪儿， 什么      

For affirmative sentences, only 都 is used.  

什么 + 都   
谁 + 都      
哪儿 + 都     

e.g.  
我什么水果都喜欢。     

For negative sentences, 都 or 也 can be used.    

谁 + 也    

e.g. 
我什么也不想做。     
谁也没见过他。    

\  

******      
  
## Test question        

你哪儿不舒服？   
我哪都不舒服。  
Where are you not feeling well?    
I'm not feeling well anywhere.  

你吃饭了吗？    
我什么也不想吃。   
Have you eaten?    
I don't want to eat anything.    

现在谁和你在一起？    
现在谁都不在这儿。    
Who is with you now?  
No one is here now.  
  
\  

******      
    
## Examples   



你喜欢什么水果？    
我什么水果都喜欢。   
What fruits do you like?  
I like all kinds of fruit.  

他很有名吗？  
当然。谁都认识他。   
Is he famous?  
Of course. Everyone knows him.   

你想去哪儿吃饭？  
去哪儿都可以。    
Where do you want to eat?  
I can go anywhere.    

******   

你去过长城？          
我刚到北京， 哪儿都没去过。     
Have you been to the Great Wall.      
I just arrived in Beijing, I haven't been anywhere.    

咱们去打球吧。  
我太累了。我什么也不想做。    
Let's go play ball.  
I am too tired. I don't want to do anything.  

我们的新老师是谁？ 
不知道。 谁也没见过他。   
Who is our new teacher?  
Don't know. No one has met him.    

******  

我什么都听不懂。   
I don't understand anything.  

我谁也不认识。  
I don't know anyone.  

我什么都爱吃。  
I like to eat everything.  


\  

******      
  
## Quiz  

Choose the correct meaning of the bold part.    

1.  
刚 来 的 时候， **我  什么  都 不 会   说。**    
我 一点儿 也 不 会  说。      

2.  
他 又   聪明   又  热情，**谁 都  喜欢 他。**  
每个人都喜欢他。  

3.  
我 没 戴  眼镜，**什么  也 看不见。**  
所有  的 东西 我  都  看不见。  


4.  
周 末  的 时候， **商场   里 哪儿 都 是  人。**  
商场  里 人 太 多 了。  

5.  
明天  我  一直 在家。**你  什么  时候 来 都 可以。**  

任何  时候  你 都 可以 来。  

Arrange the following words into a sentence.  

6.  
我什么都没吃  

7.  
谁都看过这本书    

8.  
他哪儿都去过  

9.  
我什么也没听见             

10.  
我怎么找也找不到  

