---
params:
  lesson: "Lesson 7.1"
  title: "Rhetorical questions 1: Isn't it ...?"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "不是 。。。 吗？"    
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

主讲老师：雷朔  

### 不是。。。吗？  
Used as a form of affirmation, i.e. did or didn't you?   
Not a negative sentence  
States the obvious or known information   
Expresses surprised and doubtful way of thinking     

\  

******      
  
## Test question        

Q: 你中午怎么没来？    
Why didn't you come at noon?    
A: 你不是说‘晚上’去吗？   
Didn't you say go at night?  

你不是说你不吃辣的菜吗？   
Didn't you say you don't eat spicy food?    

这不是你的眼镜吗？     
你的眼镜不是在这儿吗？   
Aren't these your glasses?    


\  

******      
    
## Examples   

咱们不是刚吃完晚饭吗？ 你又饿了？   
Didn't we just finish dinner? Are you hungry again?  

你不是昨天回国了吗？ 怎么还在这里？     
Didn't you return home yesterday? Why are you still here?  

老师不是刚讲完吗？ 你刚才没听到吗？    
Didn’t the teacher just finish speaking? Didn't you hear it just now?  

******  

我的书呢？  
不是在这里吗？   

老师，今天的作业神马？    
不是告诉你了吗？  

我们星期五下午去逛商场把？    
星期五下午不是有考试吗？   
Should we go shopping at the mall Friday afternoon?    
Isn’t there a test on Friday afternoon?      


\  

******      
  
## Quiz  
  
1.  
大夫，我的咳嗽又厉害了!     
你怎么还抽烟？   ________________  

我不是告诉过你别抽烟了吗？  

2.  
阿里，你又迟到了！    

不是八点上课吗？

3.  
服务员，不好意思，我忘了带钱，不能买这些东西了。  
________________？可以用微信付钱啊！  

你不是有手机吗？    


4.  
老师 ________________ ？  
不是啊，这是口语课的教室。  

这不是听力课的教室吗?  


5.  
你怎么还没走？________________？  
啊！对，我忘了！  


你不是要去看电影吗？  

Select the appropriate use of each rhetoric  
表示不满 (Express dissatisfaction)  
提醒注意  (reminder)    
表示质疑 (questioned)  

6.  
你 不是 有手机吗？  
提醒注意  (reminder)

7.  
不是八点上课吗？  
表示质疑 (questioned)    

8.  
你不是要去看电影吗？  
提醒注意  (reminder)     

9.  
我 不是告诉过你 别抽烟了吗？  
表示不满 (Express dissatisfaction)   

10.  
这不是 听力课的教室吗?  
表示质疑 (questioned)    

