---
params:
  lesson: "Lesson 3.1"
  title: "The same as: '一样'"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "一样"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

Used to describe similarities between two people or things  

Used in two scenarios with 跟， e.g。    
。。。 跟 。。。一样  

1. before the adjective or verb phrase    
。。。 一样 + ADJ/VERB (+ NOUN)    

2. at the end after nouns    
N + N 一样  

Negative form:  不一样    

\  

******      
  
## Test question        

我三十四岁。 大卫也三十四岁。 
我跟大卫一样大  
I am 34. David is also 34.   
I am as old as David.    


我喜欢打网球。 大卫也喜欢大王秀。  
我跟大卫一样也喜欢打网球。  
I also like tennis like David.  

大卫的爱好跟我一样    
David has the same hobby as me.   

我在Australia学习中文。  
大卫跟我不一样，他在中国学习中文。  
I study Chinese in Australia.  
Unlike me, David studies Chinese in China.    

\  

******      
    
## Examples   

上海今天三十五度，跟北京一样热。    
但是上海的天气跟北京不一样。上海常常下雨。  
It's 35 degrees in Shanghai today. But the weather in Shanghai is different to Beijing. It often rains in Shanghai.  

我听说上海花跟北京话不一样。    
放心吧。上海人跟北京人一样， 都会说中文。    
I heard that Shanghai dialect is different from Beiling dialect.    
Don't worry. Shanghai people and Beijing people both speak Chinese.  

我跟大卫一样，也要去上海旅行。  
Like David, I also want to travel to Shanghai.  

Melbourne的时间跟上海不一样。   
Melbourne's time is different to Shanghai's.  

我们班男人跟女人一样多。   
There are as many men as women in our class.     

\  

******      
  
## Quiz  

1.  
这件衣服的颜色跟那件衣服一样。  

2.  
我跟大卫一样大  

3.  
日本的汉字跟中国不一样。  

4.  
苹果跟香蕉一样贵。  

5.  
西安跟北京一样冷。

TRUE OR FALSE    

6.  
我跟爸爸一样高。  
TRUE    

7.  
爸爸跟妈妈一样岁。  
FALSE  

8.  
今天跟昨天一样天气。  
FALSE  

9.  
我们学校外国学生跟中国学生一样多。  
TRUE    

10.  
日本人跟中国人一样，也用筷子吃饭。  
TRUE  







