---
params:
  lesson: "Lesson 7.2"
  title: "Rhetorical questions 1: Is it ...?"            
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "难道……吗?"  
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document 
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`      

主讲老师：雷朔    

### 难道 (adverb)    
  
- Used in rhetorical sentences to emphasise tone      
- Using rhetoric to deliver emotion, such as query, astonishment, or anger        
- Used to make the speaker's attitude more clear  
- Used to express strong query or dissatisfaction when combined with 不 or 没      

Common usages  
不可能 (impossible)      
不应该 (shouldn't)  
不会的 (will not)   
不可以（can't be)    


\  

******      
  
## Test question        

难道你不认识我了嘛？   
You can't recognise me，can you?  

今天是妈妈的生日，你难道忘了吗？      
Today is mom’s birthday, have you forgotten it?        

这个同学， 你难道没看见我们在上课吗？   
This classmate, don't you see us in class?    

\  

******      
    
## Examples   

你难道不知道。。。 吗？   
Don't you know ... ?    

你有那么多衣服，难道还是没有合适的吗？  
You have so many clothes, do you still not have suitable ones?    

今天是假日，没有课，你难道不知道吗？    
Today is a holiday and there are no classes, don’t you know?    

你难道没有看通知吗？   
Didn't you read the notice?  

你不明白吗? --> 你难道不明白吗？  
Don't you understand? --> Don't you understand (rhetorical)?  
你忘了吗？--> 你难道忘了吗？  
Did you forget? --> Did you forget (emphasis)?  

******  

放这么多辣椒，难道不辣吗？    
Isn't it spicy, with so many peppers?  

你穿这么少难道不冷吗？  
Isn't it cold for you to wear so little?  

你难道没看见吗？     
Didn't you see it?  

你难道没有吗？    
Don‘t you have it?  



\  

******      
  
## Quiz  
  
1.  
他为你做了这么多事情，你真应该谢谢他。  
你难道不应该谢谢他吗？  

2.  
我不可能相信你.  
我难道会相信你吗？  

3.  
你去了中国这么久，不可能不会说汉语。  
你难道不会说汉语吗？    

4.  
这么简单的问题你应该知道。  
这么简单的问题你难道都不知道吗？  

5.  
这个人又懒又笨（stupid），你不可能跟他结婚（married）！  
你难道要跟他结婚吗？  

6.  
今天没有课，你难道不知道吗？  
T  

7.  
你难道看天气预报吗？    
F  

8.  
他说让我们十点在这里见面，怎么还没来？他难道没忘吗？  
F  

9.  
你是四川人，难道不吃辣的吗？  
T  

10.  
我要的东西呢？你难道又忘了吗？  
T   

