---
params:
  lesson: "Lesson 1.3"
  title: "Approximate numbers"    
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "多长，时间，多少, 小时, 几，多，来"
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  
  
## `r params$title`  
- 多少钱    
- 多长时间  

### Test question   
你来中国多长时间了？   
我来中国两个多月了  

你们学校有多少留学生？  
我们学校有五六千个留学生  

你每天学习多长时间的汉语？  
四个来小时  

你已经学了多少词了？ 
几百个词    

### Examples    

你每天运动多长时间？  
一两个小时      
  
增额小区的房子，租金一个月多少钱？   
六七千块

\  

******    

### Indefinite numbers        
一二 / 一两  
二三 / 两三  
三四    
四五  
五六   
六七  
七八 
八九   

Exceptions     
一两 and 两三 are used before measure words， eg.
一两个小时  or 两三本书    

零|一，九|十，and 十|十一 can't be used in succession, eg.  
我去图书馆借几本书    
I'm going to the library to borrow a few books  

我在北京住了十几年了， 是半个北京人了  
I've lived in Beijing for more than ten years, I'm half a Beijing person    

这些鞋都五折，几百块一双   
These shoes are 50% off, there are hundreds of pairs  
 
\  

******  

### 几    
- used for indefiinite numbers < 10      
- can be used alone, eg. 几本 or 十几  
- can be used for 十，百，千，万 （10， 100，1000，10000）， eg. 几万，几百   
  
几本 = 两本/三本      
十几年 = 14年/15年    
几百块 = 700块/800块    
几十块钱

\  

******  

### 多    
expresses more than a number   

Examples  

他是二十多岁  = 23-25 or > 20 years old   
He is in his 20s   

三岁多了 = 3.4, 3.5, or 3.6 years old or > 3 years old      
More than 3 years old  

六百多块 = 670, 680, 690 or > 600 kuai  
More than 600 kuai      

四块多(一斤) = 4.5(mao), 4.6, 4.7 or > 4 kuai      
More than four    
  
when using a single number, 多 goes after the measure word or noun, eg. 
三岁多  
六块多  
when using multiple numbers (>1 integer), 多 goes before the measure word or noun  
二十多岁  
五百多块    


\  

******  

### 来  
- denotes numbers bigger or smaller than the number before it, ie approximate         

十来个人 = approx 10 people    
两个来小时 = approx 2 hours      

goes before the measure word when using 十，百，千，万， eg.  
三百来块  
十来个   
一百来个  


goes after the measure word when the number is 1-9（can only use 个 or metric measure)  
八个来小时    
三斤来重  
这条鱼**两斤多重**  
  
\  

******    

## Quiz 

1.  
他今年多大了？  
他今年四岁多了。  

2.  
你有几个中国朋友？  
我有一两个中国朋友。  

3.  
这些东西有多重？  
这些东西有二十几斤。  

4.  
去上海的机票多少钱？  
五百来块钱。  

5.  
他有多高？  
他一米八多。  

6.  
她奶奶多大年纪了？  
她奶奶八十一二了。  

7.  
一百美元换多少人民币？  
一百美元换七百来块人民币。  

8.  
你来中国多长时间了？    
我来中国两年多了。  

9.  
你每天几点睡觉？  
我每天十二点多睡觉。  

10.  
你每天看多长时间的电视？  
我每天看两个来小时电视。




  

 






