---
params:
  lesson: "Useful phrases and notes"           
title: "Useful phrases and notes"        
link: "https://moocs.unipus.cn/course/373/task/27612/show"
content: "  "
email: matthew.malishev@gmail.com    
# end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document  
---
  
```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
  eval = TRUE, # run all code
  # echo = FALSE, # show code chunks in output 
  comment = "",
  tidy.opts=list(width.cutoff=100), # set width of code chunks in output
  tidy=TRUE, # make output as tidy
  message = FALSE,  # mask all messages
  warning = FALSE, # mask all warnings 
  size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  


<!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- start body -->  
  
## `r params$title`          
  
** = double check    
  
\  

## Lesson 1.1 

我想当。。。  
I want to be ...  

劳驾。  
Excuse me.   


## Lesson 4    

这个啤酒是谁的？
不是我的，我的朋友的。   
Not mine, my friends.  
  
你要哪件？  
Which one do you want (clothes)?    

你帮我挑?   
Can you help me pick/choose?    

你觉得这件什么样?  
What do you think of this item (clothes)?    

你试试吧？  
Try it?    

你觉得呢？   
What do you think/feel?  

**  
哪是合适？     
Which is suitable?  


\  

******      

## Lesson 2.2  

大家 = everyone     

\  

******      

## Lesson 2.3  

今天天气多好   
How good is the weather today  

快走吧  
Let's go  

******  

## Lesson 2.4  

我正想 。。。(V1 (+ V2))  
I was about to ...   
E.g.  
我正想去找他。  

一会儿 
For a while   
E.g.   
一会儿去  Go for a while   
一会儿就好 Just a moment   

******  

## Lesson 3.1    
  
放心吧    
Don't worry    

我听说 。。。  
I heard 。。。   

我还没习惯。   
I'm not used to it yet.  

******  

## Lesson 3.4  

一般  
Average/general  
e.g. 
我做饭很一般。   
My cooking is average.    

所以  
Therefore  

******  

## Lesson 4.2    

你自己  
我自己  
Yourself   
Myself    
e.g. 你自己去 。。。   
Go by yourself...     

******    

## Lesson 4.3  

当然可以 
Of course I can   

请你等我一会儿。   
Please wait for me for a while.      

没时间 ... 
No time to ... e.g. 没时间做饭    

******  

## Lesson 5.1  

半天 = long time （half a day)     
我等了半天。    

\  

打算 = plan/intend  
我打算去中国。  

******  

## Lesson 5.2  

很多次   
many times  
我去过很多次美国    

回个电话  
Call back （on the phone)  

******  

## Lesson 5.3  

马上  
immediately/right away  
e.g. 
我要马上回去.   
我可以马上过去。 

## Lesson 7.1  

可是  
However  
e.g.  
可是，今天下午。。。   

刚  
Just/recently    
e.g.  
咱们是刚吃完晚饭.    

## Lesson 7.2   

你难道没看见吗？     
Didn't you see it?  

你难道不知道。。。 吗？ 
Don't you know ... ?  

你难道不明白吗？    
Don't you understand?  

你难道忘了吗？    
Did you forget?    

你难道没有吗？  
Don‘t you have it?  
  
我不可能相信你.  
I can't believe you.  
  