---
params:
  lesson: "Useful phrases and notes"           
title: "Useful phrases and notes"        
link: "https://moocs.unipus.cn/course/373/task/27612/show"
content: "  "
email: matthew.malishev@gmail.com    
# end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document  
---
  
```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
  eval = TRUE, # run all code
  # echo = FALSE, # show code chunks in output 
  comment = "",
  tidy.opts=list(width.cutoff=100), # set width of code chunks in output
  tidy=TRUE, # make output as tidy
  message = FALSE,  # mask all messages
  warning = FALSE, # mask all warnings 
  size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  


<!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- start body -->  
  
## `r params$title`          
  
** = double check    
  
\  

## Lesson 1.1 

我想当。。。  
I want to be ...  

劳驾。  
Excuse me.   


## Lesson 4    

这个啤酒是谁的？
不是我的，我的朋友的。   
Not mine, my friends.  
  
你要哪件？  
Which one do you want (clothes)?    

你帮我挑?   
Can you help me pick/choose?    

你觉得这件什么样?  
What do you think of this item (clothes)?    

你试试吧？  
Try it?    

你觉得呢？   
What do you think/feel?  

**  
哪是合适？     
Which is suitable?  


\  

******      

## Lesson 2.2  

大家 = everyone     

\  

******      

## Lesson 2.3  

今天天气多好   
How good is the weather today  

快走吧  
Let's go  

******  

## Lesson 2.4  

我正想 。。。(V1 (+ V2))  
I was about to ...   
E.g.  
我正想去找他。  

一会儿 
For a while   
E.g.   
一会儿去  Go for a while   
一会儿就好 Just a moment   

******  

## Lesson 3.1    
  
放心吧    
Don't worry    

我听说 。。。  
I heard 。。。   

我还没习惯。   
I'm not used to it yet.  

******  

## Lesson 3.4  

一般  
Average/general  
e.g. 
我做饭很一般。   
My cooking is average.    

所以  
Therefore  

******  

## Lesson 4.2    

你自己  
我自己  
Yourself   
Myself    
e.g. 你自己去 。。。   
Go by yourself...     

******    

## Lesson 4.3  

当然可以 
Of course I can   

请你等我一会儿。   
Please wait for me for a while.      

没时间 ... 
No time to ... e.g. 没时间做饭    

******  

## Lesson 5.1  

半天 = long time （half a day)     
我等了半天。    

\  

打算 = plan/intend  
我打算去中国。  

******  

## Lesson 5.2  

很多次   
many times  
我去过很多次美国    

回个电话  
Call back （on the phone)  

******  

## Lesson 5.3  

马上  
immediately/right away  
e.g. 
我要马上回去.   
我可以马上过去。 

******  

## Lesson 7.1  

可是  
However  
e.g.  
可是，今天下午。。。   

刚  
Just/recently    
e.g.  
咱们是刚吃完晚饭.    

## Lesson 7.2   

你难道没看见吗？       
Didn't you see it?    

你难道不知道。。。 吗？   
Don't you know ... ?    

你难道不明白吗？    
Don't you understand?  

你难道忘了吗？    
Did you forget?    

你难道没有吗？  
Don‘t you have it?  
  
我不可能相信你.  
I can't believe you.   

## Lesson 7.3  

所有  
All  
e.g.  
我看过所有的电影。  
I have watched all the movies.  

我怎么知道呀？     
How should I know?   

这个字怎么读？     
How do you pronounce this word?  

### Lesson 7.4  

谁也没见过他。   
No one has met him.    

我什么都听不懂。   
I don't understand anything.    

我谁也不认识。  
I don't know anyone.  

我什么都爱吃。  
I like to eat everything.  

## Eating out/shopping       

Restaurants from cheap to more expensive   
餐馆儿 cānguǎnr  
饭馆儿 fànguǎnr  
餐厅 cāntīng  
酒家 jiǔjiā  
饭店 fàndiàn  
  
餐馆儿 and 饭馆儿 = oral version      

划算 worthwhile/better deal  
你买这个比较划算。    
You should buy this because it's a better deal.    

出门  
to leave the house /go out     

出口   
exit   

几  
a few/how many  
你买了几 张电影票？  
How many movie tickets did you buy?  

## Directions   

请带路。  
Please lead the way.   

留  
to stay  

## General    

用品
生活用品  
日用品   
goods/product    
household products  
basic necessities    

有的   
some    
有的人喝咖啡     
some people are drinking coffee   

不怎么样  
not so good  
我 会 跳舞 ， 但 跳 得 不 怎么样 。  

交  
to hand over/deliver/to pay/to make friends  
交朋友  
我们可以交朋友吗？  

发现   
to discover/find out  

检查  
to examine/examination  

办  
to do/setup/manage  

约  
make an appointment/approximately       

# Cooking  
好香 = smells fragrant    

******  

# Vocab  

有意思 / 没有意思	    
interesting / boring   

酷  
cool  

对了，。。。      
By the way, ...    
对了，这好价格。   

欣赏
to appreciate    

像  
(to be) like  
你好像他。    
You are like him.   

奇怪  
strange/odd  

如果  
In case   

帮助  
to help   

统一  
unite  

可能  
may/maybe(?)      

有关  
related   

让  
let/allow  

打算    
intend   

决定  
decide   

终于   
at last    

声音  
voice    

棒  
great/excellent     

打算   
to plan    

什么 
whatever  
你吃什么，我就吃什么。    
I'll eat whatever you eat.    
你看什么电影， 我就看什么电影。 
I'll watch whatever movie you watch.  

精彩  
brilliant/splendid  

难  
hard/difficult/troublesome    

容易  
easy  

量词  
量  
quantifier  
to measure     

已经  
already  
他们已经游了20分钟了  
They've already been swimming for 20 mins  

比如说 
for example   

认真 
serious/earnest  
你好认真。  

我也是这样    
Me too   

# Language   

练习  
to practice     

发音  
pronounciation  
你的发音很好。  

说到 
speak of  
说到好的中文老师， 。。。   

了解  
to understand  

没错  
correct/that's right  

语法  
grammar  

进步 
to advance/progress   
我想进步我的汉语。  

I want to improve my Chinese  
我想进步我的汉语。   

Chinese is hard. I want to practice more.  
中文很难。我想要多练习一点。    

越 / 越来   
surpass / more and more     
中文可越来越难了    
Chinese class is getting harder.  

慢慢    
slowly  
慢慢来一定会进步  
Slowly you will definitely improve  

******  

# Structure/conjugation  

### 比较   
more/-er (without needing to compare)  

他的汉语说得比较好    
He speaks Chinese rather well   
今天比较热   
Today is hotter  
在我们家妈妈比较会做饭  
In my family, my mother cooks better  

### 差不多  
almost the same (ADJ)      
北京的天气和纽约的天气差不多  
The weather in Beijing and NY are almost the same    
我们有差不多的生活目标  
We have almost the same life goals.    


### 对 。。。 来说。。。  
As far as ... is concerned ...  
- applied to the object of 对  

对我来说， 这家店的早饭又便宜又好吃    
For me, the breakfast in this shop is also cheap and delicious    

那个地方对他来说太远了   
For him, that place is too far.      

### 本来 。。。 后来 。。。  
Originally/previously ... later/after ...    
本来我觉得他很奇怪，后来发现他是个好人。  
At first I thought he was strange, but later I found out that he was a good person.    
本来我们要去Korea,后来决定去中国。    
Originally we were going to Korea, but later decided to go to China.  

### 会。。。的。。。  
Used for reassurance 
Often used with 一定 

明天的考试，你一定会考得很好的。     
You will do well in the exam tomorrow     

多练习。 你们会知道怎么说中文的。   
Practice more. You will know how to speak Chinese.  



# Time  

本来 originally  
我本来想去派对， 但是我太累就没去了。   
I orginally wanted to go to the party, but I was too tired and didn't go.    

以后  
after  

这么  
so  
??  

Time duration + 没。。。了  
我一年没看电影了。      
I haven't watched movies for one year.  
他三个天没洗澡了。   
He hasn't showered in three days   
他一星期没给他的女朋友打电话了。  
He hasn't called his girlfriend for a whole week.       

开始 
start   
他们11点10分开始游泳  

# Common phrases  


我是开玩笑的。  
I'm just kidding.  

妳是认真的吗？  
Are you serious?  


******  
Padlet  
- write about view/food/people in intro  
我们可以交个朋友吗？  
我想进步我的汉语。   

feng1jing3风景


zhao3chu1找出
zhao3dao4找到
想到
带来
在VS 到
at   to   





