---
params:
  lesson: ""   
title: "Useful phrases and notes"        
link: "https://moocs.unipus.cn/course/373/task/27612/show"
content: "  "
date: !r Sys.Date()
email: matthew.malishev@gmail.com    
# end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document  
---
  
```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
  eval = TRUE, # run all code
  # echo = FALSE, # show code chunks in output 
  comment = "",
  tidy.opts=list(width.cutoff=100), # set width of code chunks in output
  tidy=TRUE, # make output as tidy
  message = FALSE,  # mask all messages
  warning = FALSE, # mask all warnings 
  size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- start body -->  
  
## `r params$title`      
** = double check  
\  

## Lesson 4    

这个啤酒是谁的？
不是我的，我的朋友的。   
Not mine, my friends.  
  
你要哪件？  
Which one do you want (clothes)?    

你帮我挑?   
Can you help me pick/choose?    

你觉得这件什么样?  
What do you think of this item (clothes)?    

你试试吧？  
Try it?    

你觉得呢？   
What do you think/feel?  

**  
哪是合适？     
Which is suitable?  


\  

******      

## Lesson 2.2  

大家 = everyone     

\  

******      

## Lesson 2.3  

今天天气多好   
How good is the weather today  

快走吧  
Let's go  








  