---
params:
  lesson: "Lesson 3"   
  content: "Grammar"  
title: "Mandarin X Intermediate Chinese"        
link: "https://moocs.unipus.cn/course/373/task/27612/show"
email: matthew.malishev@gmail.com      
# end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document
---
  
  ```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
  eval = TRUE, # run all code
  # echo = FALSE, # show code chunks in output 
  comment = "",
  tidy.opts=list(width.cutoff=100), # set width of code chunks in output
  tidy=TRUE, # make output as tidy
  message = FALSE,  # mask all messages
  warning = FALSE, # mask all warnings 
  size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  


# `r params$title`    
\  

Content for `r params$lesson`: `r params$content`      
\  

<!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- start body -->  
  
## `r params$title`      
  
### 先 。。。 再 。。。  
First ... then ...  
你先吃，再付钱    
\  

### V + 不起  
### V + 得起  
Can't afford  
Can afford    
这碗牛肉面要五百块，我吃不起。     
\  

### 虽然。。。但是 / 可是    
Even though/Although ... But       

#### 虽然 。。。 但是  。。。  
虽然他是美国人，但是他的中文很好。    
Even though he is American, his Chinese is very good.   

#### 虽然 。。。 可是  。。。  
虽然现在是冬天，可是一点都不冷。    
Although it is winter now, it is not cold.  
\  

### 如果。。。就。。。  
If ... then ...  
* 如果 can be placed before or after the subject  
* 就 is an adverb  
如果你周末有空，我们就一起去电影。  
If you have time on the weeked, then let's go to the movies together.   
  
如果有钱，我们就可以去很多地方路行。   
If we had money, then we could travel to a lot of places.   







  