---
params:
  lesson: "Lesson 2"   
title: "Mandarin X Intermediate Chinese"        
link: "https://learning.edx.org/course/"
content: "Intro and vocab"  
email: matthew.malishev@gmail.com      
# end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document
---
  
  ```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
  eval = TRUE, # run all code
  # echo = FALSE, # show code chunks in output 
  comment = "",
  tidy.opts=list(width.cutoff=100), # set width of code chunks in output
  tidy=TRUE, # make output as tidy
  message = FALSE,  # mask all messages
  warning = FALSE, # mask all warnings 
  size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\  

\  

\  

\  


# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- ____________________________________________________________________________ -->
  <!-- start body -->  
  
## `r params$title`      

### 决定   
(decide + set/must/fix)  
to decide/determine    
我决定我要去上海念书。    
I decided that I want go to Shanghai to study.    
  
### 教书  
to teach
我想教她。    
I wanted to teach her.  

### 课程    
Class/course      
我这个学期课程很多。    
I have a lot of courses this semester.  

### 恭喜  
Congratulations  

### 完美 
(whole/finish  + beautiful)    
Perfect  

### 多大  
how old / how large       
你多大？    

### 年纪  
(year + record)   
age      
  
### 当      
to be / to become      
我的妹妹从小就想当医生。      
My sister has wanted to be a doctor since she was young.    

### 又。。。又。。。  
not only ... but also ... / both ... and ...    

这个房子又贵又不干净，我不想租。   
This house is both expensive and not clean, I don't want to rent it.    

中国菜又便宜又好吃。    
Chinese food is both cheap and delicious.   

### 是。。。的。。。  
Focus/contrast a part of a sentence (usually for past activities)      
Object often used at the beginning of sentence  
FOCUS = subject, time, place, manner, but never the object  
S + 是 + **FOCUS** + ACTIVITY + 的    

他是**昨天晚上**回家的。   
It was **last night** that he came home.      

这个手机超市买的。   
It was at the supermarket that I bought this phone.  

我是坐自行车来上课的。     
I took a bicycle to come to class.    

### 快。。。了。。。  
about to ...    
Indicates a change of state    

快下雨了。    
It's going to rain soon.  

我的朋友快要回家了。   
My friend is going home soon.  









  






  