---
params:
  lesson: "Lesson 2"
  title: "Auxiliary verbs 能，会，可以"  
  link: "https://moocs.unipus.cn/course/373/task/27612/show"
  content: "能，会，可以"
  date: !r Sys.Date()
  email: matthew.malishev@gmail.com    
  # end inputs ---------------------------------------------------------------
header-includes: \usepackage{float}
always_allow_html: yes
output:
  html_document:
    code_folding: hide
---

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\newpage   

Date: `r params$date`  
Corresponding author: `r params$email`    
\  

# `r paste0(params$lesson,": ",params$title)`    
\  

Content for `r params$lesson`  
`r params$content`      
\  

<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- ____________________________________________________________________________ -->
<!-- start body -->  

## Auxiliary verbs 能，会，可以  
- modify verbs and actions    
- negate with 不  

### 能  
- expresses ability  
- expresses possibility due to circumstance   

他不能走路  
He can't walk  
他能走路  
He can walk  

### 会    
- expresses grasp of skil from learning    
- expresses possibility    

今天不会下雨  
Today it won't rain  

### 可以   
- expresses permission  

我可以用一下你的自行车吗？   
Can i use your bike?  

Pose a question with auxiliary verbs by
- using the positive and negative form  
- using 吗


我可以不可以进去 / 我可以进去吗？  









